\chapter{Future work}
\label{chap:future-work}
%
% preface chapter
\lettrine[lines=3]{G}{iven} the results achieved, further improvements to the 
software are possible to the entire project structure. 
It will be possible to modify the neural model to make it more efficient and
precise by using new backbone networks that perform the classification with the
possibility of extracting new ones features from the pictures.
The dataset can be reviewed, expanded or calibrated for more specific
objectives, I provide images rich in detail and possibly made with hardware
dedicated.
This project has focused attention on implementation and training
of a neural network model for embededd systems, therefore on an architecture that
would give the best results.
Although a 3D dataset has been used for area shooting, in the future
for a dataset made with images captured in real life flight conditions, this
would lead to more detail and realism on the perception of the environment. 
Then improving the data provided to the process training it will be possible to
obtain a more accurate response of the model. 
In fact, please note that for the inference on the thermal images a dataset made
by FLIR, which was made with different hardware from the one used in this
project.
Making a new dataset with the use of the Lepton 2.5 camera will allow you to
capture images with a different resolution allowing to capture different
characteristics for the benefit of the results of the image analysis both in the
training phase and in response to the computer vision problem.
If on the one hand the results of the neural network are connected to the
dataset for train them, just as you can intervene by changing the
hyper-parameters of the model.
By modifying the hyper-parameters it is possible to carry out more calibrations
selective during training by changing the balance of accuracy and speed.
Although the compression offered by TensorFLow Lite is an excellent tool to
bring on devices embedded, the quantization shows a drift of the results with
respect to the uncompressed model.
Starting from the version of TensorFLow 2.0 it is possible to train the network
with quantized values. This will allow to obtain better results during the
execution of the inference and a drastic one reduction of false positives.
